Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-28 manuscript/main.tex
Add brief description of HI data and prosaic author contributions
Both of HI data description and author contributions are placeholders until we
have discussed what else should be included here.

\subsection*{Data}

\subsubsection*{Sequences}

\subsubsection*{Titers}

\jhc{Document HI titers from influenza CCs.}

@@

@@

JH.
RN.
TB.

>>>>

@@

\subsection*{Antigenic data}

Hemagglutination inhibition (HI) measurements were provided by collaborating centers from the WHO Global Influenza Surveillance and Response System.
We converted these raw two-fold dilution measurements to $log_{2}$ titer drops normalized by the corresponding $log_{2}$ autologous measurements as previously described \cite{Neher:2016hy}.

@@

JH planned experiments, implemented the final forecasting framework, analyzed results, and wrote the manuscript.
RN planned experiments and reviewed the manuscript.
TB planned experiments, implemented the initial forecasting framework, and reviewed the manuscript.
